Graph Exploration and Search

### 2017-11-08 exploratory.tex
Added preliminary on example-based methods

%!TEX root=./paper.tex
\subsection{Graph Exploration Methods (Davide)}

>>>>

%!TEX root=./paper.tex
\subsection{Exploratory Graph Analysis (Davide)}

\stitle{Example-based approaches.} 
One of the earliest attempts to bring examples as a query method is query-by-example~\citep{zloof1975query}.
The main idea was to help the user in the query formulation, allowing her to specify the shape of the results in terms of templates for tuples, i.e., examples.
Query-by-example has been lately revisited, and the use of examples have found application in graph data as well. 
The definition of example has transformed from a mere template to the representative of the intended results the user would like to have.
\emph{Examples} for a graph $G = (V,E)$ can be either \emph{set of nodes} $Q \subseteq V$, or \emph{subgraphs} $Q \subseteq G$, where with an abuse of notation $\subseteq$ indicates both set and structural inclusion.

\dnote{Describe seed-based approaches}

\dnote{Describe Exemplar queries~\citep{mottin2014exemplar}, graph Query by example~\citep{jayaram2015querying}, and PANDA~\citep{xie2017panda}}

%, where $\ell : V \cup E \to \mathcal{L}$ is a labelling function on a set of labels $\mathcal{L}$
